\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Sreenivasulu Ummadi} \\ \vspace{5pt}
    \small \href{mailto:ummadi.sreenivasulu.developer@gmail.com}{ummadi.sreenivasulu.developer@gmail.com} $|$
    \href{https://www.linkedin.com/in/sreenivasuluummadi/}{linkedin.com/in/sreenivasuluummadi/} $|$
    \href{https://github.com/sreenu-dev}{github.com/sreenu-dev} $|$
    \small +91-8639912976
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\small{Full-stack software engineer with 5+ years building customer-centric, scalable systems at Deloitte and Accenture using C\#/.NET Core, TypeScript, React, and Azure. Passionate about continuous learning and cross-functional collaboration — consistently grown through new challenges, from distributed systems architecture to pioneering multi-agent AI orchestration pipelines aligned with Microsoft Copilot design patterns. Committed to raising the engineering bar through mentorship, technical leadership, and inclusive development practices.}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#/.NET Core (Primary), TypeScript, Python, Java, JavaScript, SQL} \\
     \textbf{Frameworks}{: ASP.NET Web API, React, Angular, Spring Boot, Node.js, xUnit, NUnit} \\
     \textbf{Cloud \& Infrastructure}{: Azure (AZ-900 Certified) --- App Service, Functions, Service Bus, Cosmos DB, Azure SQL, AKS, API Management, Monitor, Redis Cache; Kubernetes, Docker} \\
     \textbf{Data \& Messaging}{: PostgreSQL, Apache Kafka, Redis, OpenTelemetry} \\
     \textbf{AI \& Automation}{: LangGraph, Multi-Agent Orchestration, pgvector, LLM Guardrails (aligned with Semantic Kernel patterns)} \\
     \textbf{Architecture}{: Microservices, Event-Driven Architecture, CQRS, Event Sourcing, Distributed Systems, System Design, OAuth2, JWT, IAM, CI/CD}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Deloitte}{Hyderabad}
      {Consultant}{June 2025 -- Present}
      \resumeItemListStart
      % Growth Mindset + Customer Impact
        \resumeItem{Adopted a growth mindset to diagnose and eliminate systemic API failure patterns in an ASP.NET Core service --- redesigning the response schema and adding structured audit logging, driving a 70\% error reduction and improving reliability for 50,000+ daily users.}
        \resumeItem{Dove deep into production query bottlenecks, proactively tuning SQL stored procedures and refactoring Entity Framework execution contexts to achieve 25\% query efficiency improvement, cutting customer-facing API latency by 800ms at peak load.}
        \resumeItem{Enhanced production observability and reduced mean-time-to-detect by 60\% by self-teaching OpenTelemetry and replacing a legacy logging mechanism with a custom structured logger --- turning a personal learning investment into a team-wide operational capability.}
        \resumeItem{Owned end-to-end delivery of a high-throughput secure asset-upload feature serving 10,000+ daily file transfers, integrating Azure Blob Storage patterns, virus scanning, and RBAC access controls with zero-downtime backward compatibility.}
      % Collaboration + One Microsoft
        \resumeItem{Partnered across 4 cross-functional teams to lead the migration from a monolithic frontend to a Micro-Frontend architecture using React and TypeScript, increasing deployment frequency 3x and eliminating cross-team coupling bottlenecks for 6 feature teams.}
        \resumeItem{Collaborated with DevOps and security teams to author Azure Kubernetes Service (AKS) deployment manifests with RBAC network policies, reducing deployment cycle time from 45 minutes to under 8 minutes.}
        \resumeItem{Raised the engineering bar by architecting comprehensive Confluence knowledge bases and onboarding systems, cutting new-engineer ramp-up from 3 weeks to 5 days and scaling the team from 8 to 15 engineers without productivity loss.}
      % Innovation + Inclusive AI (Copilot-aligned)
        \resumeItem{Pioneered a multi-agent AI orchestration system --- architecturally aligned with Microsoft Semantic Kernel patterns --- to automatically synthesize unit test suites and edge-case mock payloads, reducing manual test authorship overhead by 40\% and eliminating the need for 2 additional QA hires.}
        \resumeItem{Built an intelligent agentic monitoring assistant that parses system logs, identifies anomalous patterns, and surfaces real-time remediation strategies --- proactively preventing 3 production incidents in its first month and freeing engineers for higher-impact work.}
        \resumeItem{Improved feature time-to-market by 25\% by deploying LLM-driven code generation workflows, demonstrating that thoughtful AI integration compounds engineering velocity sustainably.}
      \resumeItemListEnd

    \resumeSubheading
      {Accenture}{Hyderabad}
      {Full Stack Engineering Senior Analyst}{March 2022 -- June 2025}
      \resumeItemListStart
      % Drive + Customer Focus
        \resumeItem{Delivered results at scale: shipped 100+ end-to-end user stories and high-impact features, accelerating product roadmap velocity by 25\% and improving experience for 200,000+ end users.}
        \resumeItem{Maintained 99.9\% production uptime across a system serving 100,000+ concurrent sessions, proactively debugging and resolving critical cross-stack incidents across development, testing, and live environments.}
        \resumeItem{Enhanced core application stability by debugging and resolving 300+ high-priority systemic defects across distributed environments, reducing post-release regression rates by 15\%.}
      % Growth Mindset + Accountability
        \resumeItem{Applied a growth mindset to continuously raise the codebase quality bar: instituted PR-level security scanning, achieved 95\% automated test coverage using xUnit and NUnit, and established a zero-regression production policy.}
        \resumeItem{Boosted sprint velocity and on-time feature delivery by 18\% by proactively identifying and mitigating development bottlenecks --- demonstrating accountability for team outcomes beyond my own sprint tasks.}
      % Collaboration + Mentoring (One Microsoft)
        \resumeItem{Invested in team growth: mentored 5 junior engineers through structured pairing, weekly architecture reviews, and knowledge-sharing sessions --- 2 were promoted to senior roles within 18 months, demonstrating that raising others compounds long-term team velocity.}
        \resumeItem{Streamlined cross-functional alignment by leading project steering meetings and the RFC process, cutting feature design phases by 20\% through inclusive stakeholder engagement across engineering, product, and QA teams.}
      % Customer + Inclusive Design
        \resumeItem{Championed inclusive development by leading a full WCAG 2.1 accessibility audit and remediation sprint, achieving 100\% compliance and expanding the accessible user base --- embedding accessibility checks into the PR pipeline to prevent future regressions.}
      \resumeItemListEnd

    \resumeSubheading
      {Accenture}{Bengaluru}
      {Full Stack Engineering Analyst}{September 2020 -- March 2022}
      \resumeItemListStart
        \resumeItem{Boosted application maintainability and reduced cross-device rendering latency by 20\% by designing modular, scalable Angular (v8+) and TypeScript front-end architectures serving 50,000+ mobile users.}
        \resumeItem{Accelerated page load speeds by 35\% and optimized cross-device responsiveness by refactoring asset delivery pipelines and eliminating client-side rendering bottlenecks.}
        \resumeItem{Reduced end-to-end data synchronization latency by 30\% by collaborating with back-end engineering teams to integrate high-throughput RESTful APIs built on ASP.NET Core.}
        \resumeItem{Increased sprint velocity by 15\% by driving agile practices including sprint planning, code reviews, and daily stand-ups --- modeling the collaborative, high-standard engineering culture I wanted the team to embody.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Distributed Event-Driven Ledger} $|$ \emph{.NET Core, Apache Kafka, Redis, PostgreSQL, Kubernetes}}{Jan 2026 -- Mar 2026}
          \resumeItemListStart
            \resumeItem{Architected a fault-tolerant financial ledger microservice implementing CQRS and Event Sourcing patterns to ingest 20,000+ concurrent transactions per second without data loss --- designed to production-grade reliability standards.}
            \resumeItem{Eliminated transactional race conditions and double-spending vulnerabilities using a Redis distributed lock (Redlock algorithm), guaranteeing exactly-once transaction semantics across distributed nodes.}
            \resumeItem{Optimized read-path latency by 40\% by separating command and query pipelines, utilizing Kafka consumers to asynchronously update a read-optimized PostgreSQL replica.}
            \resumeItem{Documented every design decision and failure mode in detail; 3 junior engineers used this repository as a learning resource for distributed systems patterns --- turning personal exploration into team education.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Enterprise GenAI Compliance Guardrail Engine} $|$ \emph{Python, LangGraph, OpenTelemetry, pgvector, Azure}}{March 2026 -- May 2026}
          \resumeItemListStart
            \resumeItem{Self-taught LangGraph and multi-agent AI orchestration to build an autonomous compliance pipeline --- architecturally aligned with Microsoft Semantic Kernel patterns --- achieving 94\% accuracy in regulatory intent classification.}
            \resumeItem{Reduced LLM inferencing costs by 30\% and cut compliance report generation time by 35\% using Azure Cache for Redis semantic caching and parallel multi-agent evaluation chains.}
            \resumeItem{Mitigated prompt injection risks and model hallucinations by building structural validation middleware that checks LLM outputs against strict schemas --- raising the reliability bar for production AI systems.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Resilient API Gateway} $|$ \emph{Node.js, Express, Redis, Docker, Azure Kubernetes Service}}{May 2026 -- Present}
          \resumeItemListStart
            \resumeItem{Designed a high-availability API Gateway using the Strangler and Aggregation patterns to safely decompose monolithic endpoints into AKS-hosted microservices with zero customer-facing downtime.}
            \resumeItem{Mitigated cascading backend failures under 15,000 simulated requests per minute by implementing distributed Circuit Breaker algorithms and token-bucket rate limiters.}
            \resumeItem{Implemented graceful fallback using Azure Cache for Redis to serve stale cached data during downstream outages --- prioritizing end-user experience over strict cache freshness.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Karunya University}{Coimbatore, Tamilnadu}
      {Bachelor of Technology in Computer Science and Engineering}{2020}
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
 \resumeItemListStart
  \resumeItem{AZ-900: Microsoft Azure Fundamentals}
  \resumeItem{AI-900: Microsoft Azure AI Fundamentals}
 \resumeItemListEnd

%-----------ACCOMPLISHMENTS-----------
\section{Accomplishments}
 \resumeItemListStart
  \resumeItem{ACE'22 Performer of the Year Award --- Accenture}
  \resumeItem{ACE'23 Extra Mile Award for Offshore Individual --- Accenture}
  \resumeItem{FY26 Applause Award --- Deloitte}
\resumeItemListEnd

\end{document}
